---
title: "Semaglutide DR Cohort Method Results - Sensitivity Analysis #1"
author: "Erik Westlund"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DT)
library(DBI)
library(glue)
library(kableExtra)
library(RPostgres)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(xlsx)


if(!file.exists("env.R")) stop("env.R not found")

source("env.R")

# Create postgres connection
con <- DBI::dbConnect(RPostgres::Postgres(), dbname = db_name, host = db_host, port = db_port, user = db_user, password = db_password,   options=paste0("-c search_path=", db_schema))

# List tables in schema
tables <- DBI::dbListTables(con, schema = db_schema)

# Database meta data and c
dbMeta <- DBI::dbGetQuery(con, "SELECT * FROM database_meta_data") |> 
  filter(cdm_source_abbreviation == cdmSourceAbbrev)


```

This will produce data and graphics for the Cohort Method estimation. SCSS will be put together separately.

## Databases Available

```{r databases, echo=FALSE}
databases <- DBI::dbGetQuery(con, "SELECT * FROM database_meta_data") |> 
  select(cdm_source_name, cdm_source_abbreviation, cdm_holder, database_id) 

databases |> kable()
```

## Database nicknames

We will map long database names to short ones for publication. Please confirm these are right.

```{r database_nicknames, echo=FALSE}

dbMap <- list(
  "Epic Legacy CUMC MERGE" = "CUMC",
  "JHME" = "JHME",
  "Merative CCAE" = "CCAE",
  "Merative MDCD" = "MDCD",
  "Merative MDCR" = "MDCR",
  "OHSU" = "OHSU",
  "Optum EHR" = "Optum® EHR",
  "OPTUM Extended SES" = "Clinformatics®",
  "PharMetrics" = "PharMetrics",
  "STARR" = "STARR",
  "USC" = "USC",
  "VA-OMOP" = "VA",
  "WashU" = "WU"
)

# Make df. key = col 1, val = col 2. remove row names
dbMapDf <- data.frame(
  long = names(dbMap),
  short = unlist(dbMap)
)

dbMapDf |> kable(row.names = FALSE)

# Merge in short name
databases <- databases |> 
  left_join(dbMapDf, by = c("cdm_source_abbreviation" = "long")) |> 
  rename(database_short_name = short)


dbMapOrder <- list(
  "Epic Legacy CUMC MERGE" = 3,
  "JHME" = 4,
  "Merative CCAE" = 1,
  "Merative MDCD" = 5,
  "Merative MDCR" = 6,
  "OHSU" = 7,
  "Optum EHR" = 8,
  "OPTUM Extended SES" = 2,
  "PharMetrics" = 9,
  "STARR" = 10,
  "USC" = 11,
  "VA-OMOP" = 12,
  "WashU" = 13
)

dbOrderDf <- data.frame(
  long = names(dbMapOrder),
  order = unlist(dbMapOrder)
)

databases <- databases |> 
  left_join(dbOrderDf, by = c("cdm_source_abbreviation" = "long")) |> 
  arrange(order)

```

## Outcomes

Outcomes:

* Proliferative diabetic retinopathy (Cohort ID: `17706`)
* Treatment-requiring Diabetic Retinopathy or Macular Edema including vitrectomy (Cohort ID: `17788`)

## Treatment/Comparator Exposure Pairs

For 1st the sensitivity analysis, we will compare the following treatments and comparators.


* `17803`:	New user of semaglutide with prior T2DM and prior metformin and no insulin vs.
* `17804`:	New user of empagliflozin with prior T2DM and prior metformin and no insulin

--

* `17803`:	New user of semaglutide with prior T2DM and prior metformin and no insulin vs.	
* `17805`:	New user of sitagliptin with prior T2DM and prior metformin and no insulin 

--

* `17803`:	New user of semaglutide with prior T2DM and prior metformin and no insulin	
* `17806`:	New user of glipizide with prior T2DM and prior metformin and no insulin

--

* `17803`:	New user of semaglutide with prior T2DM and prior metformin and no insulin
* `17807`:	New user of dulaglutide with prior T2DM and prior metformin and no insulin

--

* `17803`:	New user of semaglutide with prior T2DM and prior metformin and no insulin	
* `17808`:	New user of exenatide with prior T2DM and prior metformin and no insulin

We will grab these from the `cmTcList.csv` file.

```{r tcs, echo=FALSE}

outcomeIds <- c(
  17788, # Treatment-requiring Diabetic Retinopathy or Macular Edema including vitrectomy
  17706  # Proliferative diabetic retinopathy
)

cohortIds <- c(
  "New user of semaglutide with prior T2DM and prior metformin and no insulin" = 17803,
  "New user of empagliflozin with prior T2DM and prior metformin and no insulin" = 17804,
  "New user of sitagliptin with prior T2DM and prior metformin and no insulin" = 17805,
  "New user of glipizide with prior T2DM and prior metformin and no insulin" = 17806,
  "New user of dulaglutide with prior T2DM and prior metformin and no insulin" = 17807,
  "New user of exenatide with prior T2DM and prior metformin and no insulin" = 17808
)

cohortIds_DT <- c(
  17803,
  17804,
  17805,
  17806,
  17807,
  17808
)


cohortCombinations_DT <-  readr::read_csv("https://raw.githubusercontent.com/ohdsi-studies/SemaglutideNaion/refs/heads/master/inst/cmTcList.csv")
cohortCombinations <- readr::read_csv("https://raw.githubusercontent.com/ohdsi-studies/SemaglutideNaion/refs/heads/master/inst/cmTcList.csv") |> 
  filter(target_cohort_id %in% cohortIds, comparator_cohort_id %in% cohortIds) |> 
  rename(
    target_name = target_cohort_name,
    comparator_name = comparator_cohort_name
  ) |> 
  select(target_cohort_id, target_name, comparator_cohort_id, comparator_name) |> 
  mutate(comparison_name = glue("{target_name} vs. {comparator_name}")) 

cohortCombinations |> kable(row.names = TRUE)
```

## Passed Diagnostics

The following diagnostics exist for every T/C pair by outcome and datbaase:

* Maximum standardized mean difference (unshared and shared, see: https://ohdsi.github.io/CohortMethod/articles/MultipleAnalyses.html)
* Equipoise
* MDDR
* EASE

These are stored in `cm_diagnostic_summary`. We will visualize only those that pass all diagnostics. To determine whether all pass, we rely upon the `unblind` flag.

```{r diagnostics_data, echo=FALSE}

allDiagnosticsSql <- "
  SELECT * FROM cm_diagnostics_summary;
"

allDiagnostics <- DBI::dbGetQuery(con, allDiagnosticsSql)
```

The following T/C pairs pass all results according to `unblind`.

```{r passed-diagnostics, echo=FALSE}

allPassedData <- allDiagnostics |> 
  mutate(
    database_id = as.character(database_id),
    target_id = as.double(target_id),
    comparator_id = as.double(comparator_id)
  ) |> 
  mutate(
    all_pass = balance_diagnostic == "PASS" & shared_balance_diagnostic == "PASS" & equipoise_diagnostic == "PASS" & mdrr_diagnostic == "PASS" & ease_diagnostic == "PASS"
  ) |> 
 filter(
   unblind == 1
 )

summarizedDiagnosticData <- allPassedData |> 
  filter(
    target_id %in% cohortIds & comparator_id %in% cohortIds,
    outcome_id %in% c(17706, 17788)
  ) |> 
  mutate(
    database_id = as.character(database_id),
    target_id = as.double(target_id),
    comparator_id = as.double(comparator_id),
    outcome_name = case_when(
      outcome_id == 17706 ~ "Proliferative diabetic retinopathy",
      outcome_id == 17788 ~ "Treatment-requiring Diabetic Retinopathy or Macular Edema including vitrectomy"
    )
  ) |> 
  inner_join(cohortCombinations, by = c("target_id" = "target_cohort_id", "comparator_id" = "comparator_cohort_id")) |> 
  inner_join(databases, by = "database_id")


summarizedDiagnosticDataSummary <- summarizedDiagnosticData |>
  select(
    outcome_name, database_short_name, comparison_name, unblind
  ) |> 
  arrange(outcome_name, database_short_name, comparison_name)


summarizedDiagnosticDataSummary |> kable()
```

## Results

We will grab only data for the passed diagnostics. Reported risk ratios, CI bounds, and p-values are from **calibrated results**.

```{r results_data, echo=FALSE}

resultsSql <- "
  SELECT * FROM cm_result;
"

# Only include passed diagnostics T/C Pairs
matchedResults <- DBI::dbGetQuery(con, resultsSql) |> 
  mutate(
    database_id = as.character(database_id),
    target_id = as.double(target_id),
    comparator_id = as.double(comparator_id)
  ) |> 
  inner_join(summarizedDiagnosticData |> select(database_id, outcome_id, target_id, comparator_id), by = c("database_id", "outcome_id", "target_id", "comparator_id"))


rrVsCalibratedRr <- matchedResults |> 
  # filter(
  #   target_outcomes != 0 & comparator_outcomes != 0
  # ) |> 
  select(database_id, outcome_id, target_id, comparator_id,  rr, calibrated_rr, p, calibrated_p) |> 
  mutate(
    rr_cal_diff = rr - calibrated_rr,
    abs_rr_cal_diff = abs(rr_cal_diff),
      outcome_name = case_when(
      outcome_id == 17706 ~ "Proliferative diabetic retinopathy",
      outcome_id == 17788 ~ "Treatment-requiring Diabetic Retinopathy or Macular Edema including vitrectomy"
    )
  ) |> 
  inner_join(cohortCombinations |> select(target_cohort_id, comparator_cohort_id, comparison_name), by = c("target_id" = "target_cohort_id", "comparator_id" = "comparator_cohort_id")) |> 
  inner_join(databases |> select(database_id, database_short_name), by = "database_id") |>
  select(database_short_name, outcome_name, comparison_name, rr, p, calibrated_rr, calibrated_p, rr_cal_diff, abs_rr_cal_diff)
  
  
presentationResults <-  matchedResults |> 
  mutate(
    database_id = as.character(database_id),
    target_id = as.double(target_id),
    comparator_id = as.double(comparator_id),
    outcome_name = case_when(
      outcome_id == 17706 ~ "Proliferative diabetic retinopathy",
      outcome_id == 17788 ~ "Treatment-requiring Diabetic Retinopathy or Macular Edema including vitrectomy"
    )
  ) |> 
    inner_join(cohortCombinations, by = c("target_id" = "target_cohort_id", "comparator_id" = "comparator_cohort_id")) |> 
    inner_join(databases, by = "database_id") |> 
  select(
    database_id, database_short_name, outcome_id, outcome_name, target_id, target_name, comparator_id, comparator_name, comparison_name, calibrated_rr, calibrated_ci_95_lb, calibrated_ci_95_ub, calibrated_p, target_subjects, comparator_subjects, target_days, comparator_days, target_outcomes, comparator_outcomes
  )


formatPresentationResults <- function(df) {
  df |> 
  select(
    database_short_name, outcome_name,comparison_name, target_subjects, target_days, comparator_days, target_outcomes, comparator_outcomes, calibrated_rr, calibrated_ci_95_lb, calibrated_ci_95_ub, calibrated_p
  ) |> 
  rename(
    "database_name" = database_short_name,
    "n" = target_subjects,
    "hr" = calibrated_rr,
    "hr_lb" = calibrated_ci_95_lb,
    "hr_ub" = calibrated_ci_95_ub,
    "p" = calibrated_p
  ) |> 
  mutate(
    hr = round(hr, 3),
    hr_lb = round(hr_lb, 3),
    hr_ub = round(hr_ub, 3),
    p = round(p, 3)
  ) |> 
  arrange(database_name, outcome_name, comparison_name, hr)
}

```

## Risk ratio vs calibrated risk ratio 

```{r rr-vs-calibrated-rr, echo=FALSE}

rrVsCalibratedRr |>
  arrange(-abs_rr_cal_diff) |>
  kable()

```

### Correlation of RR vs Calibrated RR

```{r rr-vs-calibrated-rr-correlation, echo=FALSE}
print(cor(rrVsCalibratedRr$rr, rrVsCalibratedRr$calibrated_rr))
```

### Summary of differences between RR and Calibrated RR

```{r rr-vs-calibrated-rr-diff, echo=FALSE}

summary(rrVsCalibratedRr$rr_cal_diff) 

```

## Results with passed diagnostics but no either 0 Target or Comparator outcomes

```{r display-results, echo=FALSE}

presentationResultsHasNoOutcomes <- presentationResults |> 
  filter(
    is.na(target_outcomes) | is.na(comparator_outcomes) | target_outcomes == 0 | comparator_outcomes == 0
  )

presentationResultsHasNoOutcomes |> DT::datatable(
  options = list(
    pageLength = 5,
    scrollX = TRUE
  )
)


```

## Results for T/C pairs with passed diagnostics and at least 1 Target and Comparator outcomes

```{r display-results-again, echo=FALSE}

presentationResultsHasOutcomes <- presentationResults |> 
  filter(
    target_outcomes != 0 & comparator_outcomes != 0
  )

presentationResultsHasOutcomes |> DT::datatable(
  options = list(
    pageLength = 20,
    scrollX = TRUE
  )
)
  
```

## Evidence Synthesis Results

To get the Bayesian random-effects synthesis, we need to pull results outs from the `es_cm_result` table for the relevant outcomes. We only want results for those that passed diagnostics, which are saved in the `es_cm_diagnostics_summary` table.

We again rely upon `unblind` to decide whether a result should be presented.

```{r display-es-results, echo=FALSE}

esDiagnosticSummarySql <- "
  SELECT * from es_cm_diagnostics_summary
"

allEsDiagnosticResults <- dbGetQuery(con, esDiagnosticSummarySql) |> 
  filter(outcome_id %in% outcomeIds) |> 
  filter(target_id %in% cohortIds & comparator_id %in% cohortIds) |>
  mutate(
      mdrr_result = paste0(round(mdrr, 2), " (", stringr::str_to_lower(mdrr_diagnostic), ")"),
      ease_result = paste0(round(ease, 2), " (", stringr::str_to_lower(ease_diagnostic), ")"),
      tau_result = paste0(round(tau, 2), " (", stringr::str_to_lower(tau_diagnostic), ")"),
      all_pass = mdrr_diagnostic == "PASS" & ease_diagnostic == "PASS" & tau_diagnostic == "PASS"
    ) |> 
    inner_join(cohortCombinations, by = c("target_id" = "target_cohort_id", "comparator_id" = "comparator_cohort_id")) |> 
    mutate(
      outcome_name = case_when(
        outcome_id == 17706 ~ "Proliferative diabetic retinopathy",
        outcome_id == 17788 ~ "Treatment-requiring Diabetic Retinopathy or Macular Edema including vitrectomy"
      )
    )


allEsDiagnosticResultsPresentation <- allEsDiagnosticResults |>
    select(outcome_name, comparison_name, mdrr_result, ease_result, tau_result, unblind) |> 
  arrange(outcome_name, comparison_name)

allEsDiagnosticResultsPresentation |> kable()

diganosticSummary <- data.frame(
  allEsDiagnosticResults |>
    group_by(outcome_name) |>
    summarise(
      n = n(),
      n_pass = sum(all_pass),
      pass_rate = n_pass / n
    )
)

diganosticSummary |> kable()

```

We'll grab results only for passed diagnostics relying upon `unblind.`

```{r es-results, echo=FALSE}

allEsResultsSql = "
  SELECT * from es_cm_result
"

esResults <- dbGetQuery(con, allEsResultsSql) |> 
  filter(outcome_id %in% outcomeIds) |> 
  filter(target_id %in% cohortIds & comparator_id %in% cohortIds)

passedEsResults <- allEsDiagnosticResults |> 
  filter(unblind == 1) |>
  inner_join(esResults, by = c("outcome_id", "target_id", "comparator_id")) |> 
  select(
    outcome_id, outcome_name, target_id, target_name, comparator_id, comparator_name, comparison_name, target_subjects, target_days, comparator_days, target_outcomes, comparator_outcomes, calibrated_rr, calibrated_ci_95_lb, calibrated_ci_95_ub, calibrated_p
  ) 

```

## T/C Results, single table, pared down

Please note these are *calibrated* values.

```{r display-results-compact, echo=FALSE}


mainResults <- presentationResultsHasOutcomes |> 
  select(
    database_id, database_short_name, outcome_id, outcome_name, target_id, target_name, comparator_id, comparator_name, comparison_name, target_subjects, target_days, comparator_days, target_outcomes, comparator_outcomes, calibrated_rr, calibrated_ci_95_lb, calibrated_ci_95_ub, calibrated_p
  ) |> 
  mutate(
    target_outcomes = as.character(target_outcomes),
    comparator_outcomes = as.character(comparator_outcomes),
    target_outcomes = if_else(target_outcomes == "-5", "<5", target_outcomes),
    comparator_outcomes = if_else(comparator_outcomes == "-5", "<5", comparator_outcomes)
  ) |> 
  rename(
    database_name = database_short_name,
    target_cohort_id = target_id,
    comparator_cohort_id = comparator_id,
    group_n = target_subjects,
    hr = calibrated_rr,
    hr_lb = calibrated_ci_95_lb,
    hr_ub = calibrated_ci_95_ub,
    p = calibrated_p
  )

esResults <-  passedEsResults |>
      mutate(
      database_id = "1",
      database_name = "Bayesian Synthesis",
    )  |> 
  rename(
    target_cohort_id = target_id,
    comparator_cohort_id = comparator_id,
    group_n = target_subjects,
    hr = calibrated_rr,
    hr_lb = calibrated_ci_95_lb,
    hr_ub = calibrated_ci_95_ub,
    p = calibrated_p
  ) |>
   select(database_id, database_name, outcome_id, outcome_name, target_cohort_id, target_name, comparator_cohort_id, comparator_name, comparison_name, group_n, target_days, comparator_days, target_outcomes, comparator_outcomes, hr, hr_lb, hr_ub, p)

savedResults <- rbind(mainResults, esResults) |> 
  arrange(outcome_name)


savedResults |> 
  select(
    database_name, outcome_name, comparison_name, group_n, target_days, comparator_days, target_outcomes, comparator_outcomes, hr, hr_lb, hr_ub, p
  ) |>
  mutate(
    hr = round(hr, 2),
    hr_lb = round(hr_lb, 2),
    hr_ub = round(hr_ub, 2),
    p = round(p, 3)
    
  ) |> 
  kable()


# Save the results
xlsx::write.xlsx(savedResults, "results-cm-sensitivity-analysis-1_030225.xlsx")
saveRDS(savedResults, "results-cm-sensitivity-analysis-1.rds")


```