---
title: "Semanvamd - CM - for Cindy et al."
author: "Diep Tran"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: inline
---

## Import libraries and setting up connection 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DT)
library(DBI)
library(glue)
library(kableExtra)
library(RPostgres)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(xlsx)
library(readr)

if(!file.exists("semanvamd_env.R")) stop("semanvamd_env.R not found")

source("semanvamd_env.R")

# Create postgres connection
con <- DBI::dbConnect(RPostgres::Postgres(), dbname = db_name, host = db_host, port = db_port, user = db_user, password = db_password,   options=paste0("-c search_path=", db_schema))

# List tables in schema
tables <- DBI::dbListTables(con, schema = db_schema)

# Database meta data and c
dbMeta <- DBI::dbGetQuery(con, "SELECT * FROM database_meta_data") |> 
  filter(cdm_source_abbreviation == cdmSourceAbbrev)
```

## Databases Available

```{r databases, echo=FALSE}
databases <- DBI::dbGetQuery(con, "SELECT * FROM database_meta_data") |> 
  select(cdm_source_name, cdm_source_abbreviation, cdm_holder, database_id) 

databases |> kable()
```

## Database nicknames

We will map long database names to short ones for publication. Please confirm these are right.

```{r database_nicknames, echo=FALSE}

dbMap <- list(
  "CUIMC" = "CUIMC",
  "JHME" = "JHME",
  "Merative CCAE" = "CCAE",
  "Merative MDCD" = "MDCD",
  "Merative MDCR" = "MDCR",
  "OHSU" = "OHSU",
  "Optum EHR" = "Optum® EHR",
  "OPTUM Extended SES" = "Clinformatics®",
  "STARR" = "STARR",
  "USC" = "USC",
  "VA-OMOP" = "VA",
  "WashU" = "WU"
)

# Make df. key = col 1, val = col 2. remove row names
dbMapDf <- data.frame(
  long = names(dbMap),
  short = unlist(dbMap)
)

dbMapDf |> kable(row.names = FALSE)

# Merge in short name
databases <- databases |> 
  left_join(dbMapDf, by = c("cdm_source_abbreviation" = "long")) |> 
  rename(database_short_name = short)


dbMapOrder <- list(
  "CUIMC" = 3,
  "JHME" = 4,
  "Merative CCAE" = 1,
  "Merative MDCD" = 5,
  "Merative MDCR" = 6,
  "OHSU" = 7,
  "Optum EHR" = 8,
  "OPTUM Extended SES" = 2,
  "STARR" = 9,
  "USC" = 10,
  "VA-OMOP" = 11,
  "WashU" = 12
)

dbOrderDf <- data.frame(
  long = names(dbMapOrder),
  order = unlist(dbMapOrder)
)

databases <- databases |> 
  left_join(dbOrderDf, by = c("cdm_source_abbreviation" = "long")) |> 
  arrange(order)
```

## Diagnostics Stats

For each database, for both sensitive and specific PDR phenotypes, for each target/comparator pair, we need:

-   Maximum standardized mean difference
-   Equipoise
-   MDDR
-   Attrition fraction
-   EASE

These are stored in `cm_diagnostic_summary`, so lets first pull all that data out. We'll then manipulate it into the results we need.

```{r diagnostics_data, echo=FALSE}

allDiagnosticsSql <- "
  SELECT * FROM cm_diagnostics_summary;
"

allDiagnostics <- DBI::dbGetQuery(con, allDiagnosticsSql)
```

## Treatment vs. Comparator pairs

These cohorts are not defined in the study package, but exist in the database. Do we need to document how these are run somewhere?

We are going to select:

Prior T2DM, Prior metformin

Drug exposure: Semaglutide (GLP-1 RA), Dulaglutide (GLP-1 RA), Exenatide (GLP-1 RA), Empagliflozin (SGLT2 inhibitor), Sitagliptin (DPP4 inhibitor), Glipizide (sulfonylurea), Drug used as 2nd-line treatment

```{r tc-pairs, echo=FALSE}
cohortIds <- c(
   "Semaglutide" = 201,
   "Dulaglutide" = 211,
   "Exenatide" = 212,
   "Empagliflozin" = 213,
   "Sitagliptin" = 214,
   "Glipizide" = 215
)

cohortCombinations <- expand.grid(cohortIds, cohortIds) |> as.data.frame()
names(cohortCombinations) <- c("target_cohort_id", "comparator_cohort_id")

cohortCombinations$target_name <- cohortCombinations$target_cohort_id |> map_chr(~names(cohortIds)[.x]) |> names()
cohortCombinations$comparator_name <- cohortCombinations$comparator_cohort_id |> map_chr(~names(cohortIds)[.x]) |> names()

# Filter self-comparisons and reorder
cohortCombinations <- cohortCombinations |> 
  filter(target_cohort_id != comparator_cohort_id) |>
  select(target_cohort_id, target_name, comparator_cohort_id, comparator_name) |> 
  mutate(comparison_name = glue("{target_name} vs. {comparator_name}")) |> 
  arrange(target_cohort_id)

cohortCombinations |> kable(row.names = TRUE)

# Get only those in cmTcList.csv
cohortCombinationsFromCmTc <- readr::read_csv("https://raw.githubusercontent.com/ohdsi-studies/SemaglutideNvamd/main/inst/cmTcList.csv") 
#https://raw.githubusercontent.com/ohdsi-studies/SemaglutideNaion/refs/heads/master/inst/cmTcList.csv

# Only get those that are in cmTcList.csv
cohortCombinations <- cohortCombinations |> 
  filter(target_cohort_id %in% cohortCombinationsFromCmTc$target_cohort_id & 
           comparator_cohort_id %in% cohortCombinationsFromCmTc$comparator_cohort_id)

cohortCombinations |> kable(row.names = TRUE)

```

```{r diagnostics-helpers, echo=FALSE}
getTCDiagnostics <- function(targetId, comparatorId, outcomeId) {
  allDiagnostics |> 
    filter(
      target_id == targetId,
      comparator_id == comparatorId,
      outcome_id == outcomeId
    ) |> 
    mutate(
      database_id = as.character(database_id),
      target_id = as.double(target_id),
      comparator_id = as.double(comparator_id)
    ) |> 
    inner_join(databases, by = "database_id") |>
    inner_join(cohortCombinations, by = c("target_id" = "target_cohort_id", "comparator_id" = "comparator_cohort_id")) |> 
    mutate(
      max_sdm_result = paste0(round(max_sdm, 2), " (", stringr::str_to_lower(balance_diagnostic), ")"),
      shared_max_sdm_result = paste0(round(shared_max_sdm, 2), " (", stringr::str_to_lower(shared_balance_diagnostic), ")"),
      equipoise_result = paste0(round(equipoise, 2), " (", stringr::str_to_lower(equipoise_diagnostic), ")"),
      mdrr_result = paste0(round(mdrr, 2), " (", stringr::str_to_lower(mdrr_diagnostic), ")"),
      attrition_fraction_result = paste0(round(attrition_fraction, 2), " (", stringr::str_to_lower(attrition_diagnostic), ")"),
      ease_result = paste0(round(ease, 2), " (", stringr::str_to_lower(ease_diagnostic), ")"),
      all_pass = if_else(shared_balance_diagnostic == "PASS" & equipoise_diagnostic == "PASS" & mdrr_diagnostic == "PASS" & ease_diagnostic == "PASS", "Yes", "No"),
      all_pass_or_not_evaluated = if_else(
        (shared_balance_diagnostic == "PASS" | shared_balance_diagnostic == "NOT_EVALUATED") &
        (equipoise_diagnostic == "PASS" | equipoise_diagnostic == "NOT_EVALUATED") &
        (mdrr_diagnostic == "PASS" | mdrr_diagnostic == "NOT_EVALUATED") &
        (ease_diagnostic == "PASS" | ease_diagnostic == "NOT_EVALUATED"), "Yes", "No"
      ),
      shared_sdm_pass_sdm_fail = if_else(shared_balance_diagnostic == "PASS" & balance_diagnostic == "FAIL", "Yes", "No"),
      shared_sdm_fail_sdm_pass = if_else(shared_balance_diagnostic == "FAIL" & balance_diagnostic == "PASS", "Yes", "No"),
    ) |>
    select(
      comparison_name, database_short_name, max_sdm_result, shared_max_sdm_result, equipoise_result, mdrr_result, ease_result, all_pass, all_pass_or_not_evaluated, shared_sdm_pass_sdm_fail, shared_sdm_fail_sdm_pass, unblind
    ) |> 
    arrange(comparison_name, database_short_name)
}


aggregateResults <- function(outcomeId) {
  results <- data.frame()
  
  for(i in 1:nrow(cohortCombinations)) {
    row <- cohortCombinations[i,]
    targetId <- row$target_cohort_id
    comparatorId <- row$comparator_cohort_id
    
    results <- bind_rows(results, getTCDiagnostics(targetId, comparatorId, outcomeId))
  }
  
  results
}

processForSaving <- function(df) {
  df |> 
    select(comparison_name, database_short_name, shared_max_sdm_result, equipoise_result, mdrr_result, ease_result, all_pass) |> 
    mutate(
      comparison_name = if_else(duplicated(comparison_name), "", comparison_name)
    )
}

outcomeIds <- c(
  1, # Specific NVAMD	
  2	 # Sensitive NVAMD
)
```

## Specific NVAMD

```{r sensitive_pdr, echo=FALSE}

results <- aggregateResults(1)

results |> DT::datatable(options = list(pageLength = 20))

totalPass <- results |> filter(all_pass == "Yes") |> nrow()
totalFail <- results |> filter(all_pass == "No") |> nrow()
total <- nrow(results)

summary <- data.frame(
  total = total,
  total_pass = totalPass,
  total_fail = totalFail,
  pass_rate = round(totalPass / total, 2)
)

summary |> kable(row.names = FALSE)

xlsx::write.xlsx(processForSaving(results), "study-diagnostics_cm_specific_NVAMD.xlsx")

```

## Sensitive NVAMD

```{r specific_pdr, echo=FALSE}

results <- aggregateResults(2)
results |> DT::datatable(options = list(pageLength = 20))

totalPass <- results |> filter(all_pass == "Yes") |> nrow()
totalFail <- results |> filter(all_pass == "No") |> nrow()
total <- nrow(results)

summary <- data.frame(
  total = total,
  total_pass = totalPass,
  total_fail = totalFail,
  pass_rate = round(totalPass / total, 2)
)

summary |> kable(row.names = FALSE)

xlsx::write.xlsx(processForSaving(results), "study-diagnostics_cm_sensitive_nvamd.xlsx")

```
