---
title: "Semanvamd - SCSS - for Cindy et al."
author: "Diep Tran"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(DT)
library(DBI)
library(glue)
library(kableExtra)
library(RPostgres)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(tibble)
library(xlsx)

if(!file.exists("semanvamd_env.R")) stop("semanvamd_env.R not found")

source("semanvamd_env.R")

# Create postgres connection
con <- DBI::dbConnect(RPostgres::Postgres(), dbname = db_name, host = db_host, port = db_port, user = db_user, password = db_password,   options=paste0("-c search_path=", db_schema))

# List tables in schema
tables <- DBI::dbListTables(con, schema = db_schema)

# Database meta data and c
dbMeta <- DBI::dbGetQuery(con, "SELECT * FROM database_meta_data") |> 
  filter(cdm_source_abbreviation == cdmSourceAbbrev)

dbMeta|> kable()
```

## Databases Available

```{r databases, echo=FALSE}
databases <- DBI::dbGetQuery(con, "SELECT * FROM database_meta_data") |> 
  select(cdm_source_name, cdm_source_abbreviation, cdm_holder, database_id) 

databases |> kable()
```

## Database nicknames

We will map long database names to short ones for publication. Please confirm these are right.

```{r database_nicknames, echo=FALSE}

dbMap <- list(
  "CUIMC" = "CUIMC",
  "JHME" = "JHME",
  "Merative CCAE" = "CCAE",
  "Merative MDCD" = "MDCD",
  "Merative MDCR" = "MDCR",
  "OHSU" = "OHSU",
  "Optum EHR" = "Optum® EHR",
  "OPTUM Extended SES" = "Clinformatics®",
  "STARR" = "STARR",
  "USC" = "USC",
  "VA-OMOP" = "VA",
  "WashU" = "WU"
)

# Make df. key = col 1, val = col 2. remove row names
dbMapDf <- data.frame(
  long = names(dbMap),
  short = unlist(dbMap)
)

dbMapDf |> kable(row.names = FALSE)

# Merge in short name
databases <- databases |> 
  left_join(dbMapDf, by = c("cdm_source_abbreviation" = "long")) |> 
  rename(database_short_name = short)


dbMapOrder <- list(
  "CUIMC" = 3,
  "JHME" = 4,
  "Merative CCAE" = 1,
  "Merative MDCD" = 5,
  "Merative MDCR" = 6,
  "OHSU" = 7,
  "Optum EHR" = 8,
  "OPTUM Extended SES" = 2,
  "STARR" = 9,
  "USC" = 10,
  "VA-OMOP" = 11,
  "WashU" = 12
)

dbOrderDf <- data.frame(
  long = names(dbMapOrder),
  order = unlist(dbMapOrder)
)

databases <- databases |> 
  left_join(dbOrderDf, by = c("cdm_source_abbreviation" = "long")) |> 
  arrange(order)


```

## Diagnostics Stats

For each database, for both sensitive and specific PDR phenotypes, for each target/comparator pair, we need:

-   MDRR (MDRR diagnostic)
-   EASE (EASE diagnostic)
-   Time trend (time trend diagnostic)
-   Pre-exposure (pre-exposure diagnostic)

These are stored in `sccs_diagnostic_summary`, so lets first pull all that data out. We'll then manipulate it into the results we need.

Below is the first few rows of the diagnostics table.

```{r diagnostics_data, echo=FALSE}

allDiagnosticsSql <- "
  SELECT * FROM sccs_diagnostics_summary;
"

allDiagnostics <- DBI::dbGetQuery(con, allDiagnosticsSql)

allDiagnostics |> head() |> kable()

```

## Exposures

We will need to filter down the diagnostics for the outcome-exposure pairs we care about.

Note that SCCS uses different cohort IDs than the CDM. Here are the mappings:

```{r tc-pairs, echo=FALSE}

cohortIds <- c(
 "Semaglutide" = 101,
 "Dulaglutide" = 102,	
 "Exenatide" = 103,
 "Empagliflozin" = 104,
 "Sitagliptin" = 105,
 "Glipizide" = 106
)

exposures <- cohortIds |> 
  enframe(name = "exposure", value = "cohort_id") |> 
  mutate(exposure = as.character(exposure))
 
exposures |> kable()

```

## Outcomes

Outcome IDs remain the same.

```{r outcomes, echo=FALSE}

outcomeIds <- c(
  "Specific NVAMD" = 1, 
  "Sensitive NVAMD" = 2  
)

outcomes <- outcomeIds |> 
  enframe(name = "outcome", value = "cohort_id") |> 
  mutate(outcome = as.character(outcome))

outcomes |> kable()

```

## Exposure Outcome Set ID vs. Outcome

To get the diagnostics for an exposure-outcome pairing, you need to the `exposures_outcome_set_id`.

First, get the `exposures_outcome_set_id` from the `sccs_exposures_outcome_set` table matching each outcome.

Then, to figure out what exposure each `exposures_outcome_set_id` corresponds to, you need to match the `exposures_outcome_set_id` from the `sccs_exposures_outcome_set` table to the `exposures_outcome_set_id` in the `sccs_exposures` table, and match the `era_id` from the `sccs_exposures` table to the `cohort_id` for our exposure.

```{r exposure_outcome_set, echo=FALSE}

exposureSetSql <- "
  SELECT * FROM sccs_exposures_outcome_set
"

allExposureSets <- DBI::dbGetQuery(con, exposureSetSql)

exposureSets <- allExposureSets |> 
  filter(outcome_id %in% outcomes$cohort_id) |>
  inner_join(outcomes, by = c("outcome_id" = "cohort_id")) |>
  select(outcome, outcome_id, exposures_outcome_set_id)

exposureSets |> kable()


```

To get the exposure-outcome set ID for pairing, you need to match the `exposures_outcome_set_id` from the `sccs_exposures_outcome_set` table to the `exposures_outcome_set_id` in the `sccs_exposure` table.

```{r exposure_sccs_outcome_set, echo=FALSE}

sccsExposuresSql <- "
  SELECT * FROM sccs_exposure
"

allScssExposures <- DBI::dbGetQuery(con, sccsExposuresSql)

exposureOutcomePairs <- exposureSets |> 
  inner_join(allScssExposures, by = c("exposures_outcome_set_id" = "exposures_outcome_set_id")) |> 
  inner_join(exposures, by = c("era_id" = "cohort_id")) |>
  select(outcome_id, outcome, era_id, exposure, exposures_outcome_set_id) |> 
  arrange(outcome_id)

exposureOutcomePairs |> kable()

```

## Diagnostis for each exposure/outcome pair

With this information, we can now get the diagnostics for each exposure/outcome pair.

```{r diagnostics, echo=FALSE}

studyDiagnostics <- allDiagnostics |> 
  filter(exposures_outcome_set_id %in% exposureOutcomePairs$exposures_outcome_set_id) |>
  inner_join(databases |> select(database_id, database_short_name), by = c("database_id" = "database_id")) |> 
  inner_join(exposureOutcomePairs |> select(exposures_outcome_set_id, outcome_id, outcome, exposure, era_id), by = c("exposures_outcome_set_id")) |> 
  rename(exposure_id = era_id)


```

```{r diagnostics-helpers, echo=FALSE}
getExposureDiagnostics <- function(exposureId, outcomeId) {
  studyDiagnostics |> 
    filter(
      exposure_id == exposureId,
      outcome_id == outcomeId
    ) |> 
   mutate(
      mdrr_result = paste0(round(mdrr, 2), " (", stringr::str_to_lower(mdrr_diagnostic), ")"),
      ease_result = paste0(round(ease, 2), " (", stringr::str_to_lower(ease_diagnostic), ")"),
      time_trend_result = paste0(round(time_trend_p, 2), " (", stringr::str_to_lower(time_trend_diagnostic), ")"),
      pre_exposure_result = paste0(round(pre_exposure_p, 2), " (", stringr::str_to_lower(pre_exposure_diagnostic), ")"),
      all_pass = if_else(mdrr_diagnostic == "PASS" & ease_diagnostic == "PASS" & time_trend_diagnostic == "PASS" & (pre_exposure_diagnostic == "PASS" | pre_exposure_diagnostic == "NOT EVALUATED"), "Yes", "No")
    ) |>
    select(
      exposure, database_short_name, mdrr_result, ease_result, time_trend_result, pre_exposure_result, all_pass, unblind
    ) |> 
    arrange(exposure, database_short_name)
}


aggregateResults <- function(outcomeId) {
  results <- data.frame()
  
  for(i in 1:nrow(exposures)) {
    exposureId <- exposures$cohort_id[i]
    results <- bind_rows(results, getExposureDiagnostics(exposureId, outcomeId))
  }
  
  results
}

processForSaving <- function(df) {
  df |> 
    select(exposure, database_short_name, mdrr_result, ease_result, time_trend_result, pre_exposure_result, all_pass) |> 
    mutate(
      exposure = if_else(duplicated(exposure), "", exposure)
    )
}

outcomeIds <- c(
  1, # Specific NVAMD
  2  # Sensitive NVAMD	
)
```

## Specific NVAMD

```{r sensitive_pdr, echo=FALSE}

results <- aggregateResults(1)
results |> DT::datatable(options = list(pageLength = 20))

totalPass <- results |> filter(all_pass == "Yes") |> nrow()
totalFail <- results |> filter(all_pass == "No") |> nrow()
total <- nrow(results)

summary <- data.frame(
  total = total,
  total_pass = totalPass,
  total_fail = totalFail,
  pass_rate = round(totalPass / total, 2)
)

summary |> kable(row.names = FALSE)

xlsx::write.xlsx(processForSaving(results), "semanvamd-study-diagnostics_sccs_SpecificNVAMD.xlsx")

```

## Sensitive NVAMD

```{r specific_pdr, echo=FALSE}


results <- aggregateResults(2)
results |> DT::datatable(options = list(pageLength = 20))

totalPass <- results |> filter(all_pass == "Yes") |> nrow()
totalFail <- results |> filter(all_pass == "No") |> nrow()
total <- nrow(results)

summary <- data.frame(
  total = total,
  total_pass = totalPass,
  total_fail = totalFail,
  pass_rate = round(totalPass / total, 2)
)

summary |> kable(row.names = FALSE)

xlsx::write.xlsx(processForSaving(results), "semanvamd-study-diagnostics_sccs_SensitiveNVAMD.xlsx")


```
